\chapter*{Acknowledgement}
\label{chap:acknowledgement}
\addcontentsline{toc}{chapter}{\nameref{chap:acknowledgement}}

We would like to express our sincere gratitude and appreciation to the Department of Computer Engineering, Faculty of Engineering at Kasetsart University. The department provided us with a foundation in software development and technical knowledge, as well as the essential facilities and opportunities required to bring this project to fruition.

We extend our deepest appreciation to our advisor, Assoc. Prof. Dr. Chaiporn Jaikaeo, for his invaluable mentorship and technical direction. His expertise in networking and system design was instrumental during the Research and Design phases, and his constant feedback ensured the integrity and efficiency of our project.

We are also highly indebted to Assoc. Prof. Dr. Punpiti Piamsa-nga, Head of the Department, for his administrative support and for fostering an environment that encourages innovation and practical problem-solving within the Software Engineering program.

Last but certainly not least, we would like to thank our faculty professors and instructors who have shared their valuable knowledge and insights throughout our academic journey. Their dedication to teaching the intricate details of Software and Knowledge Engineering provided us with the critical thinking skills necessary to navigate the challenges of this project. Finally, we thank our families and peers for their unwavering encouragement and support during the completion of our degree.


\vspace{.2in}
\begin{flushright}
    \usevar{\srsAuthorOne} \\
    \usevar{\srsAuthorTwo} \\
    \usevar{\srsAuthorThree}
\end{flushright}